\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-07-01 paper.tex
Typos

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of her actions and also to synchronise seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognise simple elemntary actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Human-Robot Interaction is and is going to remain a challenging field for
Artificial Intelligence. We hope that this contribution helps with clarifying
of these challenges and making them concrete decisional problems.

@@

This work has been partially supported by EU FP7 "CHRIS" (grant 215805) and ``SAPHARI'' (grant ICT-287513) projects, and the EU H2020 Marie Sklodowska-Curie Actions project DoRoThy (grant 657227).

>>>>

Monitoring human activity is needed by the execution controllers to track the
engagement of the human and the progress of her actions and also to synchronise seamlessly
its own actions with the human actions. Full human action
and activity recognition is a task that requires knowledge and reasoning both on
high-level facts like goals, intentions and plans, as well as bottom-up data
from human and object motions. {\sc Spark} implements a set of simple temporal and
geometric heuristics on human hand trajectories and possible objects placements
to recognise simple elementary actions. Those primitive actions are assessed through
monitoring situations like ``an empty hand is close to an object on a table''
(precursor for a \emph{pick}), or ``a hand holding an object is over a
container'' (precursor for a \emph{throw}).  {\sc Spark} recognises a set of
such primitives. When combined with the other geometric computations and a predictive
plan of the human actions (see Section~\ref{hatp}), the execution controller can
track the fulfilment of the pre- and post-conditions of the predicted human
actions. As a result, the robot can monitor the engagement of the human and the
overall progress of the human-robot shared plan.

@@

Human-Robot Interaction is and is going to remain a challenging field for
Artificial Intelligence. We hope that this contribution helps with clarifying
these challenges and making them concrete decisional problems.

@@

This work has been partially supported by EU FP7 CHRIS (grant 215805) and
SAPHARI (grant ICT-287513) projects, and the EU H2020 Marie Sklodowska-Curie
Actions project DoRoThy (grant 657227).
